Appendix to "Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2024-12-07 src/docs_paper-jtb/appendix.Rmd
Copy over from old paper

```{r echo = FALSE}
options(scipen = 100)

@@

```{r}
point_summary <- read_csv("depends/point-estimates.csv")

point_summary <- point_summary %>%
  mutate(type = fct_recode(type, "Output" = "output", "Latent" = "latent"))

latex_table_point_estimates <- function(.indicator) {
  point_summary %>%
  group_by(par, type, indicator, method) %>%
  summarise(
    rmse = sqrt(mean((truth - approximate)^2)),
    mae = mean(abs(truth - approximate))
  ) %>%
  ungroup() %>%
  pivot_wider(
    names_from = "method",
    values_from = c("rmse", "mae")
  ) %>%
  filter(indicator == .indicator) %>%
  select(Parameter = par, Type = type, `TMB` = `rmse_TMB`, `PCA-AGHQ` = `rmse_PCA-AGHQ`) %>%
  mutate(
    Difference = `PCA-AGHQ` - TMB,
    `Percent Difference` =  (`PCA-AGHQ` - TMB) / TMB
  ) %>%
  gt::gt(groupname_col = "Type") %>%
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    n_sigfig = 2
  ) %>%
 gt::fmt_percent(
    columns = `Percent Difference`,
    decimals = 1
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) %>%
  gt::as_latex() %>%
  as.character()
}

latex_table_point_estimates("Posterior mean estimate") %>%
  cat(file = "point-summary-mean.tex")

latex_table_point_estimates("Posterior SD estimate") %>%
  cat(file = "point-summary-sd.tex")
```

@@

ks_summary %>%
  ungroup() %>%
  filter(type == "Latent") %>%
  select(-type) %>%
  select(Parameter = parname, TMB, `PCA-AGHQ` = aghq) %>%
  mutate(Difference = `PCA-AGHQ` - TMB) %>%
  gt::gt() %>%
  gt::summary_rows(
   columns = c(`TMB`, `PCA-AGHQ`, Difference),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  ) %>%
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    decimals = 3
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Difference"),
    fn = function(x) ifelse(x < 0, paste0("\\textbf{", x, "}"), paste0(x))
  ) %>%
  gt::as_latex() %>%
  as.character() %>%
  cat(file = "ks-summary.tex")
```

@@

n_divergent <- np %>%
  filter(Parameter == "divergent__") %>%
  summarise(n_divergent = sum(Value)) %>%
  pull(n_divergent)

@@

<!-- ```{r algorithm-flowchart, fig.cap="Flowchart describing the algorithm we propose (work in progress)."} -->
<!-- knitr::include_graphics("depends/algorithm-flowchart.pdf") -->
<!-- ``` -->

>>>>

```{r echo = FALSE, message = FALSE}
library(dplyr)

options(scipen = 100)

@@

```{r}
point_summary <- readr::read_csv("depends/point-estimates.csv")

point_summary <- point_summary |>
  mutate(type = forcats::fct_recode(type, "Output" = "output", "Latent" = "latent"))

latex_table_point_estimates <- function(.indicator) {
  point_summary |>
  group_by(par, type, indicator, method) |>
  summarise(
    rmse = sqrt(mean((truth - approximate)^2)),
    mae = mean(abs(truth - approximate))
  ) |>
  ungroup() |>
  tidyr::pivot_wider(
    names_from = "method",
    values_from = c("rmse", "mae")
  ) |>
  filter(indicator == .indicator) |>
  select(Parameter = par, Type = type, `TMB` = `rmse_TMB`, `PCA-AGHQ` = `rmse_PCA-AGHQ`) |>
  mutate(
    Difference = `PCA-AGHQ` - TMB,
    `Percent Difference` =  (`PCA-AGHQ` - TMB) / TMB
  ) |>
  gt::gt(groupname_col = "Type") |>
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    n_sigfig = 2
  ) |>
 gt::fmt_percent(
    columns = `Percent Difference`,
    decimals = 1
  ) |>
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) |>
  gt::as_latex() |>
  as.character()
}

latex_table_point_estimates("Posterior mean estimate") |>
  cat(file = "point-summary-mean.tex")

latex_table_point_estimates("Posterior SD estimate") |>
  cat(file = "point-summary-sd.tex")
```

@@

ks_summary |>
  ungroup() |>
  filter(type == "Latent") |>
  select(-type) |>
  select(Parameter = parname, TMB, `PCA-AGHQ` = aghq) |>
  mutate(Difference = `PCA-AGHQ` - TMB) |>
  gt::gt() |>
  gt::summary_rows(
   columns = c(`TMB`, `PCA-AGHQ`, Difference),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  ) |>
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    decimals = 3
  ) |>
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) |>
  gt::text_transform(
    locations = gt::cells_body("Difference"),
    fn = function(x) ifelse(x < 0, paste0("\\textbf{", x, "}"), paste0(x))
  ) |>
  gt::as_latex() |>
  as.character() |>
  cat(file = "ks-summary.tex")
```

@@

n_divergent <- np |>
  filter(Parameter == "divergent__") |>
  summarise(n_divergent = sum(Value)) |>
  pull(n_divergent)

@@
